Fig1

### 2020-02-21 analysis/figure-1.Rmd
smaller font

abcd <- plot_grid(a,b,c,d, nrow = 1, labels = c("b", "c", "d", "e"), label_size = 12 )

@@

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 12, rel_heights = c(0.5,1))

@@

hij <- plot_grid(h,i,j, nrow = 1, labels = c("h", "i", "j"), label_size = 12)

>>>>

abcd <- plot_grid(a,b,c,d, nrow = 1, labels = c("b", "c", "d", "e"), label_size = 8 )

@@

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 8, rel_heights = c(0.5,1))

@@

hij <- plot_grid(h,i,j, nrow = 1, labels = c("h", "i", "j"), label_size = 8)
